% PlanetMath proposal draft for arXiv:2602.19578
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Ultrafilter operads and condensed symmetry}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.19578, "Ultrafilter operads and condensed symmetry" (2026-02-22)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Ultrafilter operads combine condensed logoi with ultrafilter completions to encode profinite symmetries. The authors:
\begin{enumerate}
  \item construct operads inside span logoi of condensed sets endowed with ultrafilters;
  \item describe how condensed Galois actions act on such operads;
  \item classify the resulting algebras via fixed points of ultrafilter correspondences; and
  \item apply the recipe to condensed tori and $p$-adic fields.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 467479] Number-theory spans used to motivate the Galois fixed-point analysis.
  \item[MO 467887] Geometric-group spans illustrating condensed symmetries.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 506448] "Ultrafilters inside condensed mathematics".
  \item[Math.SE 508200] "Operads controlling profinite symmetry".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item Review condensed sets/logoi and ultrafilter completions.
  \item Define ultrafilter operads via span logoi and list the compatibility axioms.
  \item Describe the Galois action and fixed-point classification (MO 467479/467887).
  \item Present the condensed torus example referencing Math.SE 506448.
  \item Summarize consequences for $p$-adic symmetry and Math.SE 508200.
\end{enumerate}
\subsection*{Action items}
Sync arXiv source, pull MO embeddings (467479, 467887), pull Math.SE embeddings (506448, 508200), and expand the PlanetMath entry accordingly.
