% PlanetMath proposal draft for arXiv:2602.19172
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Factorization weaves for stratified $(\infty,1)$-topoi}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.19172, "Factorization weaves for stratified $(\infty,1)$-topoi" (2026-02-20)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
The authors introduce "factorization weaves" as hybrid data combining exit-path $\infty$-categories with factorization homology on stratified spaces. Highlights:
\begin{enumerate}
  \item Construction of weaves via iterated correspondences in exit-path topoi,
  \item classification theorem comparing weaves with constructible cosheaves, and
  \item examples for arboreal singularities and Morse campers.
\end{enumerate}
For PlanetMath we will:
\begin{itemize}
  \item translate the new terminology into existing exit-path + factorization homology entries,
  \item showcase a worked example on stratified surfaces, and
  \item document how the authors use spans to encode excision.
\end{itemize}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 467167] Thread on algebraic geometry + curves referencing exit-path ideas.
  \item[MO 466647] Question on Picard groups and spans; provides another example of correspondences.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 470112] "How to compute exit-paths for a simple stratification?"
  \item[Math.SE 475389] "Factorization homology on bouquets of circles".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item Review of stratified $(\infty,1)$-topoi and exit-path $\infty$-categories.
  \item Definition of factorization weaves.
  \item Classification theorem and proof sketch.
  \item Worked example (stratified surface) + references to MO/Math.SE threads.
  \item Bibliography + cross-links.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull arXiv source into futon6 proof-state.
  \item Use storage/mo-processed-gpu embeddings for MO 467167 and MO 466647.
  \item Fetch Math.SE thread embeddings for 470112 and 475389 from storage/math-processed-gpu.
  \item Write the PlanetMath draft after aligning terminology with existing entries.
\end{itemize}
