% PlanetMath proposal draft for arXiv:2602.19205
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Operadic coends for polynomial monads}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.19205, "Operadic coends for polynomial monads" (2026-02-20)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
This submission analyzes coend formulas for polynomial monads and their algebras. It covers:
\begin{enumerate}
  \item coend presentations for free algebras,
  \item compatibility with Day convolution and base-change, and
  \item a categorified Beck-Chevalley condition for operadic spans.
\end{enumerate}
PlanetMath focus areas:
\begin{itemize}
  \item define "polynomial monad" and "operadic coend" with pm dictionary words,
  \item provide a sample computation for the associative operad, and
  \item note how Beck-Chevalley appears in the proofs.
\end{itemize}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 466703] Big-list question on category theory references that includes operadic spans.
  \item[MO 467551] (reuse) interplay between Green functions and spans, relevant for polynomial functors.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 468744] "Coends for simple polynomial functors".
  \item[Math.SE 473012] "Day convolution vs operad substitution".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item Review polynomial monads + operadic spans.
  \item Statement of the coend formula and necessary hypotheses.
  \item Beck-Chevalley + Day convolution compatibility.
  \item Worked example (associative operad and dendroidal sets).
  \item Cross-links to MO and Math.SE references.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Sync arXiv TeX into futon6 proof-state.
  \item Extract MO thread summaries (466703, 467551) from storage/mo-processed-gpu.
  \item Pull Math.SE embeddings (468744, 473012) from storage/math-processed-gpu.
  \item Draft PlanetMath entry + EDN after aligning notation.
\end{itemize}
