% PlanetMath proposal draft for arXiv:2602.19604
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Sheafified correspondences for spectral stacks}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.19604, "Sheafified correspondences for spectral stacks" (2026-02-22)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Sheafified correspondences endow spans with quasicoherent sheaves and use them to encode power operations on spectral stacks. The authors:
\begin{enumerate}
  \item form a monoidal category $\mathrm{Corr}^\mathrm{shv}(\mathcal{X})$ by decorating every leg of a span with a quasicoherent sheaf;
  \item construct power operations and norm functors from these sheafified spans;
  \item compare the resulting structure with spectral Mackey functors; and
  \item work out examples for spectral Deligne--Mumford stacks.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 466615] Measure-theoretic spans illustrating how decorations behave.
  \item[MO 467167] Algebraic-geometry spans guiding the spectral stack example.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 509312] "Quasicoherent sheaves on spectral stacks".
  \item[Math.SE 510448] "Mackey functors built from spans".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item Recall spectral stacks and discuss Math.SE 509312.
  \item Define sheafified spans and the monoidal convolution.
  \item Record the construction of power operations/norms with references to MO 466615.
  \item Compare with spectral Mackey functors and cite Math.SE 510448.
  \item Provide the spectral Deligne--Mumford stack example inspired by MO 467167.
\end{enumerate}
\subsection*{Action items}
Pull arXiv source, fetch MO embeddings (466615, 467167), fetch Math.SE embeddings (509312, 510448), and prepare the expanded entry.
