% PlanetMath proposal draft for arXiv:2602.19532
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Warped Kan extensions for indexed $(\infty,1)$-categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.19532, "Warped Kan extensions for indexed $(\infty,1)$-categories" (2026-02-22)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Warped Kan extensions add span data to the usual Kan-extension calculus in an indexed $\infty$-category $\mathcal{E}\to \mathcal{B}$. The authors:
\begin{enumerate}
  \item package correspondences between fibers of $\mathcal{E}$ into a bicategory of spans;
  \item define warped left/right Kan extensions as coends over that bicategory;
  \item establish Beck--Chevalley and mate correspondences for the warped construction; and
  \item apply the machinery to parametrized spectra and $t$-structures.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 465935] Functional-analysis spans modeling norms, reused for Beck--Chevalley intuition.
  \item[MO 467211] Homotopy-theory thread on indexed categories ties into the parametrized spectrum example.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 503872] "Kan extensions for indexed categories".
  \item[Math.SE 505120] "Span-based Beck-Chevalley conditions".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item Recall indexed $\infty$-categories + standard Kan extensions.
  \item Introduce the warped span bicategory and define warped Kan extensions.
  \item Prove Beck--Chevalley/mate results, pointing to MO 465935 and Math.SE 505120.
  \item Detail the parametrized spectra example (MO 467211).
  \item Record consequences for $t$-structures and base-change formulas.
\end{enumerate}
\subsection*{Action items}
Ingest arXiv source, gather MO embeddings (465935, 467211), gather Math.SE embeddings (503872, 505120), then write the expanded entry.
