% PlanetMath proposal draft for arXiv:2602.19480
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Condensed limits via span logoi}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.19480, "Condensed limits via span logoi" (2026-02-20)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
The manuscript computes limits/colimits in condensed mathematics using span logoi to encode condensed symmetry. PR \#12 already contains the structural ``span logoi from condensed groups'' entry (arXiv:2602.19267); this proposal narrows to the explicit limit formulas, the condensed torus/field case studies, and the Beck--Chevalley identities so the two PlanetMath pages split \emph{framework} vs \emph{computation}. Key steps:
\begin{enumerate}
  \item construct span logoi from condensed groups and record how limits pull back along spans;
  \item prove a condensed Beck--Chevalley theorem ensuring the span calculus respects base-change;
  \item treat condensed tori and condensed fields as working examples; and
  \item connect the story to Galois symmetries highlighted in MO 466647 + MO 467599.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 466647] Picard/Picard span discussion relevant to condensed tori.
  \item[MO 467599] Finite-group spans controlling condensed symmetry constraints.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 498240] "Condensed sets vs. logoi".
  \item[Math.SE 499776] "Span correspondences in condensed mathematics".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Condensed refresher.} Review condensed logoi, summarize Math.SE 498240, and point to the span-logoi entry (2602.19267) for the abstract construction we will reference.
  \item \textbf{Limit/colimit formulas.} Define span logoi in the condensed setting, write down the condensed Beck--Chevalley theorem, and outline the explicit co/end formulas that make this entry computational.
  \item \textbf{Condensed torus example.} Carry out the torus computation in detail, explaining how MO 466647 supplies Picard-span input and how condensed norms appear.
  \item \textbf{Galois symmetry + condensed fields.} Describe the finite-group symmetry application (MO 467599) and explain how the formulas specialize to condensed fields and $p$-adic coefficients.
  \item \textbf{Cross-link + future work.} Document how these calculations feed back into the span-logoi article without duplication and list the downstream PlanetMath pages (condensed fields, condensed norms) that will consume the formulas.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Sync the arXiv source, fetch MO embeddings (466647, 467599), and fetch Math.SE embeddings (498240, 499776).
  \item Coordinate with the 2602.19267 span-logoi draft so introductory text lives there while this entry keeps the explicit formulas and examples.
  \item Expand the PlanetMath entry following the outline and record which condensed field identities will become separate encyclopedia lemmas.
\end{itemize}
