% PlanetMath proposal draft for arXiv:2602.19655
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{$p$-adic span topoi and analytic geometries}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.19655, "$p$-adic span topoi and analytic geometries" (2026-02-22)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
The article constructs $p$-adic analytic topoi by gluing condensed spans of Huber pairs. Highlights:
\begin{enumerate}
  \item define $p$-adic span topoi whose objects are Huber pairs with span morphisms;
  \item compare the resulting topos with dagger analytic geometry;
  \item analyze the induced $p$-adic Galois action; and
  \item compute norms for condensed fields.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 467711] $p$-adic span symmetries for condensed tori.
  \item[MO 467999] Spans for surreal/field extensions, suggesting the dagger comparison.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 512064] "$p$-adic condensed geometry overview".
  \item[Math.SE 513200] "How do dagger spaces interact with spans?".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item Recap Huber pairs, condensed sets, and Math.SE 512064.
  \item Define $p$-adic span topoi and list their universal properties.
  \item Explain the dagger comparison theorem with references to MO 467999/Math.SE 513200.
  \item Describe the Galois symmetry example (MO 467711).
  \item Note consequences for condensed fields and future directions.
\end{enumerate}
\subsection*{Action items}
Sync arXiv source, pull MO embeddings (467711, 467999), pull Math.SE embeddings (512064, 513200), and expand the PlanetMath entry accordingly.
