% PlanetMath proposal draft for arXiv:2602.19510
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Hypermonadic covers in higher topos theory}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.19510, "Hypermonadic covers in higher topos theory" (2026-02-22)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Hypermonadic covers refine the notion of hypercovers by threading monadic descent data through a cohesive $\infty$-topos. The authors:
\begin{enumerate}
  \item build a tower of spans resolving a cohesive topos $\mathcal{X}$ by monadic approximations;
  \item compare the resulting hypermonadic nerve with Grothendieck topologies and show they detect the same $\infty$-connectivity;
  \item explain how condensed symmetry acts on hypermonadic covers, giving rise to spectral descent; and
  \item work out examples for condensed abelian groups, citing Math.SE 500112/502640 for background.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 466823] Gradient-flow spans inspire the resolution tower used in the definition.
  \item[MO 467143] Functional-analysis spans highlight the monadic descent argument.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 500112] "How do hypercovers appear in higher topoi?"
  \item[Math.SE 502640] "Monad descent in $(\infty,1)$-categories".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item Recall cohesive $\infty$-topoi and classical hypercovers.
  \item Define hypermonadic covers via the span resolution tower and connect to Math.SE 502640.
  \item Describe the descent theorem and cite MO 466823/467143 for intuition.
  \item Present the condensed abelian group example and link to Math.SE 500112.
  \item Summarize the consequences for spectral descent and condensed symmetry.
\end{enumerate}
\subsection*{Action items}
Pull arXiv source, fetch MO embeddings (466823, 467143), fetch Math.SE embeddings (500112, 502640), then draft the expanded entry.
