% PlanetMath proposal draft for arXiv:2602.19267
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Span logoi and condensed symmetry}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.19267, "Span logoi and condensed symmetry" (2026-02-20)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
The authors introduce "span logoi": logoi enriched by span correspondences designed for condensed mathematics. Contributions include:
\begin{enumerate}
  \item building span logoi from condensed sets and topological groups,
  \item relating them to Lurie's spectral logoi, and
  \item extracting symmetry data from span-based Galois actions.
\end{enumerate}
For PlanetMath we will ground these notions by:
\begin{itemize}
  \item mapping "span logoi" onto existing entries on logoi and condensed mathematics,
  \item detailing one example using condensed tori, and
  \item clarifying how span symmetry recovers classical Galois theory.
\end{itemize}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 466647] (Picard groups + spans) — helps motivate span symmetries.
  \item[MO 467871] Discussion of geometric group theory and spans, relevant to condensed symmetry.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 471256] "What is a condensed topos?" (ct.category-theory, gn.general-topology).
  \item[Math.SE 478504] "Span correspondences on condensed sets".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item Reintroduce logoi and condensed mathematics basics.
  \item Define span logoi and list key properties.
  \item Compare with spectral logoi.
  \item Examples involving condensed tori and Galois actions.
  \item References to the supporting MO/Math.SE material.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Load the arXiv TeX into futon6 proof-state.
  \item Pull embeddings for MO 466647 and MO 467871 from storage/mo-processed-gpu.
  \item Retrieve Math.SE embeddings for 471256 and 478504.
  \item Draft the PlanetMath EDN + TeX pair per outline.
\end{itemize}
